### 2015-04-03 doc/manual/mscviewer.tex
Added a lot more info in manual Images for manual are now automatically generated running tool in batch improved build system added generation of html manual

\documentclass[11pt, twoside, titlepage]{book}
\usepackage[hcentering,textwidth=150mm,textheight=225mm]{geometry}
\usepackage[Bjornstrup]{fncychap}
\usepackage{graphicx}
\usepackage[colorlinks=true, 
            urlcolor=blue]{hyperref}
\usepackage{mathtools} 
\usepackage{makeidx}
\makeindex

%\usepackage[margin=1in]{geometry}
\usepackage{fixltx2e} 
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{centernot}
\usepackage{listings}
\usetikzlibrary{shadows}
\usepackage[toc,page]{appendix}
\usepackage{breakurl}
\usepackage{wrapfig}
\usepackage{tcolorbox}
\usepackage{lipsum}
\include{titlepage}

\newcommand{\prog}{MSCViewer} 
\newcommand{\eventprefix}{\texttt{@msc}}
\newcommand{\mscevent}{\texttt{@msc\_event}}
\newcommand{\naive}{ na\"{\i}ve}
\newcommand{\closebutton}{\includegraphics[height=.7\baselineskip]{../../src/com/cisco/mscviewer/resources/icons/16x16/close1.png}}
\newenvironment{Sidebar}[1][r]
  {\wrapfigure{#1}{0.5\textwidth}\tcolorbox}
  {\endtcolorbox\endwrapfigure}

@@

\makeatletter
\renewcommand\tableofcontents{%
    \if@twocolumn
      \@restonecoltrue\onecolumn
    \else
      \@restonecolfalse
    \fi
    \chapter*{\contentsname}%
        \@mkboth{%
           \MakeUppercase\contentsname}{\MakeUppercase\contentsname}%
    \@starttoc{toc}%
    \if@restonecol\twocolumn\fi
    }
\makeatother

@@

\tableofcontents

@@

\section{\prog}
\prog{} is a tool supporting visualization and analysis of message sequence
charts. The tool loads a text file, interprets lines containing the
\eventprefix{} qualifier and representing events and interactions occurring on
entities, ignoring other lines. From the interpreted lines a model is
constructed in memory. In the GUI the tool can visualize the list of enties,
from which the user can select a subset to be shown in a sequence diagram chart.
through keyboard or mouse commands the user can easily navigate through events
and interactions, search, and perform a number of other actions for browsing the
diagram.

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{simple-flow.png}
  \caption{A simple flow example}
  \label{fig:simple-flow} 
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{concurrent-flow.png}
  \caption{A flow with two concurrent branches}
  \label{fig:concurrent-flow} 
\end{figure}

@@

Line 1 defines a \defterm{local} event, which is not part of any interaction
with other entities. The value of the \texttt{entity} key indicates the entity
this event belongs to. There is no explicit sytax to define an entity: as it
parses events, \prog{} creates entities the events belong to.

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex1.png}
  \caption{\prog{} GUI with \texttt{lst1.msc} loaded.}
  \label{fig:gui-lst1}
\end{figure}

Fig.~\ref{fig:gui-lst1} shows the GUI in its initial state.  The bottom-right
area shows the the input file, while the top-left tree shows the various
entities. Double-click on the \texttt{producer} and \texttt{consumer} entities
to open them in the diagram area, in the top-right part of the window
(fig.~\ref{fig:gui-lst1-open}). Each entity is shown in a column, with events
interleaving each other across entities. Columns can be sorted by dragging them
from their header (the part showing the entity name), and closed by clicking on
the   \closebutton{} button. Clicking on an event selects it; the selection can
be moved to the previous/next event for an entity by pressing respectively the
\keystroke{SHIFT} \keystroke{$\uparrow$} and \keystroke{SHIFT}
\keystroke{$\downarrow$} key combinations. To navigate from a source or
destination event to the paired event in an interaction use the 
\keystroke{SHIFT} \keystroke{$\leftarrow$} or \keystroke{SHIFT} \keystroke{$\rightarrow$}.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex1-open.png}
  \caption{The user has opened all the entities in the diagram}
  \label{fig:gui-lst1-open}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex3-cycle.png}
  \caption{Diagram with circular dependencies caused by interactions}
  \label{fig:gui-lst3}
\end{figure}

@@

%\lstinputlisting[language=Java]{../../examples/lst4.msc}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex4-time.png}
  \caption{Diagram with timestamps associated to events.}
  \label{fig:gui-lst4}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{gui-ex5-data.png}
  \caption{The Data view showing data associated to the selected event}
  \label{fig:gui-lst5}
\end{figure}

@@

\section{Input Language}
\prog{} can load a single file containing description of events for multiple
entities and build a model in memory. The input file is composed by lines of
text. \prog{} ignores any line not containing the \texttt{@msc\_event} or
\texttt{@msc\_entity} word. This allows to load trace files which might contain
a mix of trace lines catered to \prog{} and unrelated trace lines.

An event is described in the input language by a line containing the
\texttt{@msc\_event} followed by a JSON object. If the reader is not familiar
with this format, it is explained here: \href{http://json.org/}{http://json.org/}

\chapter{\prog{}  GUI}

>>>>

\documentclass[11pt, twoside, titlepage]{book}
\usepackage[hcentering,textwidth=150mm,textheight=225mm]{geometry}
\usepackage[Bjornstrup]{fncychap}
\usepackage{graphicx}
\usepackage[colorlinks=true, 
            urlcolor=blue]{hyperref}
\usepackage{mathtools} 
\usepackage{longtable}
\usepackage{makeidx}
\makeindex

%\usepackage[margin=1in]{geometry}
\usepackage{fixltx2e} 
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usepackage{centernot}
\usepackage{listings}
\usetikzlibrary{shadows}
\usepackage[toc,page]{appendix}
\usepackage{etoolbox}
\usepackage{wrapfig}
\usepackage{tcolorbox}
\usepackage{lipsum}
\include{titlepage}

\newcommand{\prog}{MSCViewer}

\newcommand{\mscevent}{\texttt{@event}}
\newcommand{\mscentity}{\texttt{@entity}}
\newcommand{\naive}{ na\"{\i}ve}
\newcommand{\closebutton}{\includegraphics[height=.7\baselineskip]{images/close1.png}}
\newcommand{\tblimg}[1]{\raisebox{-.5\height}{\includegraphics[height=.2in]{#1}}}

\newenvironment{Sidebar}[1][r]
  {\wrapfigure{#1}{0.5\textwidth}\tcolorbox}
  {\endtcolorbox\endwrapfigure}

@@

\makeatletter
\renewcommand\tableofcontents{
    \if@twocolumn
      \@restonecoltrue\onecolumn
    \else
      \@restonecolfalse
    \fi
    \chapter*{\contentsname}%
        \@mkboth{%
           \MakeUppercase\contentsname}{\MakeUppercase\contentsname}%
    \@starttoc{toc}%
    \if@restonecol\twocolumn\fi
    }
\makeatother

@@

\include{tocnotoc}

@@

\section{\prog}
\prog{} is a tool supporting visualization and analysis of message sequence
charts. The tool loads a text file, interprets lines containing the
\mscevent{} or \mscentity{} keywords and representing events and interactions occurring on
entities, ignoring other lines. From the interpreted lines a model is
constructed in memory. In the GUI the tool can visualize the list of enties,
from which the user can select a subset to be shown in a sequence diagram chart.
through keyboard or mouse commands the user can easily navigate through events
and interactions, search, and perform a number of other actions for browsing the
diagram.

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/simple-flow.png}
  \caption{A simple flow example}
  \label{fig:simple-flow} 
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/concurrent-flow.png}
  \caption{A flow with two concurrent branches}
  \label{fig:concurrent-flow} 
\end{figure}

@@

Line 1 defines a \defterm{local} event, which is not part of any interaction
with other entities. The value of the \mscentity{} key indicates the entity
this event belongs to. There is no explicit sytax to define an entity: as it
parses events, \prog{} creates entities the events belong to.

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex1.png}
  \caption{\prog{} GUI with \texttt{lst1.msc} loaded.}
  \label{fig:gui-lst1}
\end{figure}

Fig.~\ref{fig:gui-lst1} shows the GUI in its initial state.  The bottom-right
area shows the content of the input file, while the top-left tree shows the various
entities. Double-click on the \texttt{producer} and \texttt{consumer} entities
to open them in the diagram area, in the top-right part of the window
(fig.~\ref{fig:gui-lst1-open}). Each entity is shown in a column, with events
interleaving each other across entities. Columns can be sorted by dragging them
from their header (the part showing the entity name), and closed by clicking on
the   \closebutton{} button. Clicking on an event selects it; the selection can
be moved to the previous/next event for an entity by pressing respectively the
\keystroke{SHIFT} \keystroke{$\uparrow$} and \keystroke{SHIFT}
\keystroke{$\downarrow$} key combinations. To navigate from a source or
destination event to the paired event in an interaction use the 
\keystroke{SHIFT} \keystroke{$\leftarrow$} or \keystroke{SHIFT} \keystroke{$\rightarrow$}.

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex2-open.png}
  \caption{The user has opened all the entities in the diagram}
  \label{fig:gui-lst1-open}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex3-cycle.png}
  \caption{Diagram with circular dependencies caused by interactions}
  \label{fig:gui-lst3}
\end{figure}

@@

%\lstinputlisting[language=Java]{../../examples/lst4.msc}
\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex4-time.png}
  \caption{Diagram with timestamps associated to events.}
  \label{fig:gui-lst4}
\end{figure}

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.5\textwidth,natwidth=1024,natheight=600]{images/gui-ex5-data.png}
  \caption{The Data view showing data associated to the selected event}
  \label{fig:gui-lst5}
\end{figure}

@@

\section{Input Language}
\prog{} can load a single file containing description of events for multiple
entities and build a model in memory. The input file is composed by lines of
text. \prog{} ignores any line not containing the \mscevent{} or
\mscentity{} word. This allows to load trace files which might contain
a mix of trace lines catered to \prog{} and unrelated trace lines.

An event is described in the input language by a line containing the
\mscevent{} followed by a JSON object. If the reader is not familiar
with this format, it is explained here: \href{http://json.org/}{http://json.org/}

\prog interprets certain keys-value pairs in the JSON objects in order to build
the entity/event/interaction model.

For events, the following keys are interpreted:

\begin{center}
    \begin{longtable}{ll}
    \hline
    \textbf{Key:}         & \texttt{entity} \\
    \textbf{Type:}        & String \\
    \textbf{Mandatory:}   & y\\
    \textbf{Example:}     & \texttt{"id":"node0/producer\_1"}\\
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
        an identifier for the entity this event belongs to. identifiers can contain slash to indicate hierarchy of entities.\\
    \end{minipage}    
    \tabularnewline
    \hline
    \textbf{Key:}         & \texttt{label} \\
    \textbf{Type:}        & String \\
    \textbf{Mandatory:}   & y\\
    \textbf{Example:}     & \texttt{label":"operation competed"}\\
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
        a label specifying some immediate info about this event. In MSCViewer the label is shown on the right 
        of the icon representing the event.\\
    \end{minipage}    
    \tabularnewline
    \hline
    \textbf{Key:}         & \texttt{time} \\
    \textbf{Type:}        & String \\
    \textbf{Mandatory:}   & n\\
    \textbf{Example:}     & \texttt{"time":"1542532s"}\\
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
        a timestamp for the event.  It's an integer number followed by a unit qualifier: "s" (seconds), "ms" 
        (milliseconds), "us" (microseconds) or "ns" (nanoseconds). The timestamp is interpreted as elapsed time 
        since the Unix Epoch . If the timestamp is not present inside the JSON object, it is expected to be 
        present before it in one of the formats supported by syslog.  time is shown in MSCViewer at the right 
        of the event icon. \\
    \end{minipage}    
    \tabularnewline
    \hline
    \textbf{Key:}         & \texttt{type} \\
    \textbf{Type:}        & String \\
    \textbf{Mandatory:}   & n\\
    \textbf{Example:}     & \texttt{"type":"Timer"}\\
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
        If present, the value specifies a distinct type for the event. Events of different types can be rendered
         by different icons in MSCViewer. Icons can be provided by a user in a directory in the form of PNG images
          whose name matches the type name. This allows to plug domain-specific representation for events.\\
    \end{minipage}    
    \tabularnewline
    \hline
    \textbf{Key:}         & \texttt{data} \\
    \textbf{Type:}        & JSON Value\\
    \textbf{Mandatory:}   & n\\
    \textbf{Example:}     & \texttt{"data":\{"v1":10, "v2":20\}} \\
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
	    Specifies some data associated to the event. For example, if the event corresponds to the sending of 
	    a message, the value here could be a JSON representation of the message. in MSCViewer data is shown in 
	    a table in the data section when the event is selected.\\
    \end{minipage}    
   \tabularnewline
    \hline
    \textbf{Key:}         & \texttt{src} \\
    \textbf{Type:}        & JSON Value\\
    \textbf{Mandatory:}   & n\\
    \textbf{Example:}     & 
        \begin{minipage}[t]{0.8\columnwidth}%
            \texttt{"src":"producer\_1/123"},\\
            \texttt{"src":"\{"id":"producer\_1/123", "color":"00FF00"\}} 
        \end{minipage}  \\  
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
        Interactions are pairs of events. In a pair, one event contains the src key, while the other contains the 
        dst key, both with the same value. Interactions are visualized in MSCViewer as arrows going from the source
        to the destination event. The file format doesn't mandate a particular format for the value, but the value
        should be unique for an interaction (more on this in the interaction section of this document. In the 
        simplest case the value can be a string (which is a valid JSON value). When certain aspects of the 
        rendering need to be controlled, the value can be a JSON object with an "id" key identifying the unique
         interaction, and other keys (such as "color") identifying rendering aspects.\\
     \end{minipage}   
   \tabularnewline
    \hline
    \textbf{Key:}         & \texttt{dst} \\
    \textbf{Type:}        & JSON Value\\
    \textbf{Mandatory:}   & n\\
    \textbf{Example:}     & 
        \begin{minipage}[t]{0.8\columnwidth}%
            \texttt{"dst":"producer\_1/123"},\\
            \texttt{"dst":"\{"id":"producer\_1/123", "color":"00FF00"\}} 
        \end{minipage}  \\  
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
        Interactions are pairs of events. In a pair, one event contains the src key, while the other contains 
        the dst key, both with the same value. Interactions are visualized in MSCViewer as arrows going from
        the source to the destination event. The file format doesn't mandate a particular format for the value,
        but the value should be unique for an interaction (more on this in the interaction section of this 
        document. In the simplest case the value can be a string (which is a valid JSON value). When certain
        aspects of the rendering need to be controlled, the value can be a JSON object with an "id" key 
        identifying the unique interaction, and other keys (such as "color") identifying rendering aspects.\\
     \end{minipage}    
   \tabularnewline
  \hline
  \end{longtable}
\end{center}

The following table shows the keys interpreted by MSCViewer for entities:

\begin{center}
    \begin{longtable}{ll}
    \hline
    \textbf{Key:}         & \texttt{id} \\
    \textbf{Type:}        & String \\
    \textbf{Mandatory:}   & y\\
    \textbf{Example:}     & \texttt{"id":"/node0/1984"}\\
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
		The unique identifier for the entity \\
    \end{minipage}    
    \tabularnewline
    \hline
    \textbf{Key:}         & \texttt{name} \\
    \textbf{Type:}        & String \\
    \textbf{Mandatory:}   & y\\
    \textbf{Example:}     & \texttt{"id":"/node0/producer\_1"}\\
    \textbf{Description:} &
    \begin{minipage}[t]{0.8\columnwidth}%
        A name for the entity. Names don't need to be unique and provide a more human-readable representation for the entity\\    
    \end{minipage}    
    \tabularnewline
	\end{longtable}
\end{center}

\chapter{\prog{}  GUI}
This chapter provides a description of all the GUI elements in \prog.

\section{The Entities Tree}

\begin{figure}[ht!]
  \centering
  \includegraphics[width=0.3\textwidth]{images/left-pane.png}
  \caption{The Entities tree}
  \label{fig:entity-tree} 
\end{figure}

The Entities Tree is visible on the top-left are of the GUI once an input file is loaded and the \textit{Entities} tab 
is selected. This tree shows all entities defined in the input file. An entity is defined if a \mscentity{} line is 
present or if the entity is specified in the \texttt{entity} entry of a \mscevent line. Elements of an entity 
ID separated by slashes constitute nodes in the tree. Internal nodes of the tree may have event of their own, if 
they appear as the terminal element in the \texttt{entity} entry of at least one event, or not, in which case they
just represent some relationship among the child nodes. In the latter case the node is visualized in a lighter 
shade.

For example, a system may be composed by multiple processes running in different hosts. The user may decide to 
have a log file for each process, and use a \texttt{host-id/process-id} notation for entity events. In this case,
Intermediate tree nodes for host-id will be created, but clearly there will be no events associated to them.

Double-clicking on a node corresponding to an entity with at least one event opens the entity in the Sequence 
Diagram. Double-clicking on a node corresponding to an entity already opened in the Sequence Diagram causes
it to be removed from the diagram. The following legend shows the various representations of the tree nodes:

\begin{center}
    \begin{longtable}{ll}
  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/entity.png}
	& entity with at least one event, currently closed in sequence diagram\\
  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/entity_open.png}
	& entity with at least one event, currently open in sequence diagram\\
  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/entity_faded.png}
	& entity with no event, can't be opened in sequence diagram\\
	\end{longtable}
\end{center}

\section{The Sequence Diagram area}
The sequence diagram area is situated on the top-right part of the GUI. Entities can be opened in this area by
double-clicking on them in the Entity Tree. Open entities can be rearranged by dragging them from their 
header.

\section{The Tool Bar}
The toolbar contains the following buttons:

\begin{center}
    \begin{longtable}{ll}
	 \multicolumn{2}{l}{\textbf{Actions}} \\
	\hline
  	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/load.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Loads a new input file. Pressing this button causes a file chooser to open. Selecting a file and
      	pressing ok results in the file being loaded. 
       \end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/reload.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Reload the present file. This command can be used if changes are made to the file after it was loaded.
	  	Note that all currently opened entities are closed before the new file is loaded.
	  	\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/camera.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Captures a screenshot of the sequence diagram. The user can select whether to capture the entire model 
		(regardless of what entities are opened in the diagram), The entities currently opened, or just the 
		entities for which at least one event is highlighted.
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/clear_highlights.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Removes any highlight set on events or interactions, whether they're on open entity or not.
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/run.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Re-run the latest script that was executed. Scripts can be executed by double-clicking on nodes in the
		tree shown in the Script tab, but this button provides a convenient shortcut to rerun the latest script.
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/options.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Opens a window where various program options can be configured.
		\end{minipage}\\ \\

	\multicolumn{2}{l}{\textbf{Cursor Tools}} \\
	\hline
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/select.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Chooses the select tool associated to the mouse pointer. The select tool allows to select an event or
		interaction. 
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_green.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		chooses the green marker for highlighting events. When this tool is selected clicking on an event
		causes it to be highlighted in green.
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_blue.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Same as the green highlighter, but with blue color.
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_yellow.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Same as the green highlighter, but with yellow color.
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/highlight_red.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Same as the green highlighter, but with red color.
		\end{minipage}\\ \\

	\multicolumn{2}{l}{\textbf{Visualization Options}} \\
	\hline
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/blocks.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Shows/hides blocks. 
	  \end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/time.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Shows/hides event timestamps
		\end{minipage}\\ \\
	\tblimg{../../src/com/cisco/mscviewer/resources/icons/32x32/label.png}
	& \begin{minipage}[t]{0.8\columnwidth}
		Shows/hides event labels
		\end{minipage}\\ \\
	\end{longtable}  
\end{center}
